How and Why to run a Hack Week

### 2017-12-07 supplementary_material.tex
some notes

\documentclass{nature}

%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{natbib}

\usepackage{hyperref}
\usepackage{url}
\usepackage{microtype}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{tabularx}

@@

\begin{document}

@@

@@

We have worked to minimize the cost of registration for our events in order to enable broad participation, especially for participants from institutions, countries and demographics that are generally underrepresented at other meetings. Locations that offer some funding or provide free space are preferable to those that do not.
At Astro Hack Week, we have found that travel grants are of crucial importance especially to undergraduates, students from minority backgrounds and participants from underrepresented countries. During the organization of Python in Astronomy 2017, we found that minority participants disproportionally decline to attend, and often cite lack of sufficient travel funding as the primary reason. In particular if increasing diversity in the more technical aspects of a field is one of the workshop's goals, providing enough travel funding for between five to ten participants can make a significant difference in allowing minority researchers to attend.

@@

\subsection{Box 1: Impostor Syndrome}

@@

\end{document}

>>>>

%\documentclass{nature}

%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them
%\usepackage{graphicx}	% Including figure files
%\usepackage{amsmath}	% Advanced maths commands
%\usepackage{amssymb}	% Extra maths symbols
%\usepackage{natbib}

%\usepackage{hyperref}
%\usepackage{url}
%\usepackage{microtype}
%\usepackage{rotating}
%\usepackage{booktabs}
%\usepackage{threeparttable}
%\usepackage{tabularx}

@@

%\begin{document}

@@

\subsection{Event Size and Duration}

- add a few sentences about size and interaction with goals
- add a few sentences about duration and interaction with goals
- add that we're still figuring this out
- we're experimenting with length and duration

\subsubsection{Participant selection}

Add more on participant selection, especially practical details. 
- add problem of asking good questions: especially questions that require candidates to calibrate should be written in such a way that they allow for objective calibration (e.g. ask for specific actions people have taken, rather than "beginner", "intermediate", "expert"
- add other approaches taken by the three different hack weeks

- add different criteria for selection

@@

We have worked to minimize the cost of registration for our events in order to enable broad participation, especially for participants from institutions, countries and demographics that are generally underrepresented at other meetings. Locations that offer some funding or provide free space are preferable to those that do not.
At Astro Hack Week, we have found that travel grants are of crucial importance especially to undergraduates, students from minority backgrounds and participants from underrepresented countries. We found that minority participants disproportionally decline to attend, and often cite lack of sufficient travel funding as the primary reason. In particular if increasing diversity in the more technical aspects of a field is one of the workshop's goals, providing enough travel funding for between five to ten participants can make a significant difference in allowing minority researchers to attend.

@@

\subsection{Ensuring Participation}
to add here:
- things about inclusion and how to make people participate
- add sentence about that to main paper
- ANthony needs to add stuff here
- add e.g. that we planted designated question askers
- have organizers as dedicated facilitators

- want to have some good

\subsubsection{Impostor Syndrome}

@@

%\end{document}
